\TitleText

### 2021-03-21 presentation/3_simulation.tex
Fix presentation typos
Revise presentation

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Reducing the complexity}
{
\I Casting to a linear program

\I A successive estimation of the nonzero components (not used in the final set of figures)

\I Use the basis pursuit denoising form
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I Let the \m {\T {\chi}}, the relative 2-norm error, be the performance metric.

\Disp {
\NC \T {\chi}
=\NC \RB {
   \F {\VNm {\V {h} -\Hat {\V {h}}} _2}
   {\VNm {\V {h}}_2}
} _{\Ss {avg}}, \NR
}

\I Also define \m {\chi} by plugging in \m {\V {d}} into \m {\T {\chi}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (1/6)}
{
\I \m {N_H=6, N_{B,t}=3, N_{B,r}=2}, 2 stages
\blank [big]
\externalfigure [error-small-wide-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (2/6)}
{
\I \m {N_H=6, N_{B,t}=2, N_{B,r}=3}, 2 stages
\blank [big]
\externalfigure [error-small-tall-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (3/6)}
{
\I \m {N_H=12, N_{B,t}=6, N_{B,r}=4}, 2 stages
\blank [big]
\externalfigure [error-medium-wide-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (4/6)}
{
\I \m {N_H=12, N_{B,t}=4, N_{B,r}=6}, 2 stages
\blank [big]
\externalfigure [error-medium-tall-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (5/6)}
{
\I \m {N_H=18, N_{B,t}=9, N_{B,r}=6}, 2 stages
\blank [big]
\externalfigure [error-big-wide-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (6/6)}
{
\I \m {N_H=18, N_{B,t}=6, N_{B,r}=9}, 2 stages
\blank [big]
\externalfigure [error-big-tall-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS outperforms other methods in the high noise case

\I DS requires less sampling to recover for given channel instance.

\I The relaxed sparsity may have compromised effectiveness of DS.

@@

\I \m {\T {\chi}} and \m {\chi} differ by some orders of magnitude.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity}
{
\I Let \m {C} denote big-O estimation of complexity, then
\Disp {
\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log \R {N_{B,t} N_{B,r}}} \NR
\NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR
\NC C_{\Rm {DS}} =\NC \mathcal {O} \SB {N_{H}^6} \NR
}

>>>>

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Reducing the complexity}
{
\I Casting to a linear program (not used now)

\I Successively estimate the nonzero components (not used now)

\I Use the basis pursuit denoising form

\Disp {
\NC \Hat {\V {g}}
\LA \NC \Min {\V {g}'} 
\CB {
\VNm {\V {g}'} _1 
+ \l_{\Ss {DS}} \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty
} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (1/6)}
{
\I \m {N_H=6, N_{B,t}=3, N_{B,r}=2}, 2 stages
\blank [big]
\externalfigure [error-small-wide-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (2/6)}
{
\I \m {N_H=6, N_{B,t}=2, N_{B,r}=3}, 2 stages
\blank [big]
\externalfigure [error-small-tall-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (3/6)}
{
\I \m {N_H=12, N_{B,t}=6, N_{B,r}=4}, 2 stages
\blank [big]
\externalfigure [error-medium-wide-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (4/6)}
{
\I \m {N_H=12, N_{B,t}=4, N_{B,r}=6}, 2 stages
\blank [big]
\externalfigure [error-medium-tall-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (5/6)}
{
\I \m {N_H=18, N_{B,t}=9, N_{B,r}=6}, 2 stages
\blank [big]
\externalfigure [error-big-wide-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error norm (6/6)}
{
\I \m {N_H=18, N_{B,t}=6, N_{B,r}=9}, 2 stages
\blank [big]
\externalfigure [error-big-tall-two.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS outperforms other methods in the high noise case and less measurement

\I The relaxed sparsity may have compromised its effectiveness.

@@

\I Unfortunately, the values are too small to verify the asymptotic bound.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity}
{
\I Let \m {C} denote big-O estimation of complexity, then
\Disp {
\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_{B,t} N_{B,r}} \NR
\NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR
\NC C_{\Rm {DS}} =\NC \mathcal {O} \SB {N_{H}^6} \NR
}
